---
title: "README for SMI205 Assessmnet 2 template"
author: "Aneta Piekut"
date: "2023-05-22"
output:
  github_document:
    toc: true
    toc_depth: 2
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> Clone this repository in your R Studio -> New Project -> Version control.

# 1. Replication report - template

Edit `SMI205_Assessment2_Template.Rmd` by adding pieces of your work into it. It is a template prepared to help you to write a transparent research report. Your job is to make your research fully reproducible.

Publish it as a reproducible report on [Rpubs.com](https://rpubs.com/) website and create a project repository on Github (optional).

> Use your student number to name your Rpubs and Github accounts so your work is anonymous.

As any template, it can be improved, so go on and make edits so your report is even more transparent. 

## 1.1. Your Workflow 

As with other projects, organise your work transparently into a hierarchy of folders.

Project TIER Protocol 4.0 (https://www.projecttier.org/tier-protocol/protocol-4-0/) offers an excellent guide for what to include and how to organise reproduction documentation for a project based on quantitative methods.

## 1.2. Re-publishing data and code

You should not be republishing data that you have not created or substantially edited to create a new version of a dataset. 

> Check what is the licence of the data and code: https://www.sheffield.ac.uk/library/copyright/licences. It might be the licence allows remixing, tweaking, and building upon others work non-commercially. 

If you found a replication package for your chosen paper, remember to credit the original material, like R scripts, developed by other researchers. 

# 2. Rpubs version of the template

HTML version of the template is published here:
https://rpubs.com/AnetaPiekut/SMI205_Assessment2_2023_template

# 3. `renv` package

The Template.Rproj was created without using `renv` package, yet, you could consider using it. The `renv` package helps you to create a reproducible environment for your R project. Read more here: https://rstudio.github.io/renv/.

It saves information about R and loaded packages. So if you later (after any R updates or changes in the packages) or other people open your Rproj, it will install the same libraries, and will not use the central libraries installed on a computer ([Joseph 2022](https://medium.com/@adrian.joseph/renv-make-r-environment-reproducible-414d88c683aa )). 

## 3.1. How to work with `renv` package

It is likely you will need to install new packages and would like to change the saved local libraries. There are three important commands in the package to do so:

+ Call `renv::init()` to initialise a new project-local environment with a private R library.
+ Call `renv::snapshot()` to save the state of the project library to the lockfile (called renv.lock).
+ Call `renv::restore()` to recall the packages and version the last time you called `renv::snapshot()`.

They are called automatically when you work in RProj and initiate `renv` at the start.

## 3.2. Trouble shooting with `renv` package

Here is a useful guide by Joseph A. (2022). renv: make R environment reproducible. URL: https://medium.com/@adrian.joseph/renv-make-r-environment-reproducible-414d88c683aa (accessed 09/02/2023).

# 4. Transparency checklist

+ Are all files organised and saved in relevant folders?
+ Are all files, variables and R objects named and organised in a way, so their role is clear?
+ Have you created a READme file introducing your project?
+ Is a replication package or any other files provided by the authors properly referenced in your work?
+ Is your project portable? Are your directory paths relative?
+ Have you tested whether your project runs on a different device?
+ Remove from your repository any unused templates before submitting your work.
+ Make sure you save information about your workspace specifications in your READme file (see my below).
+ Before saving files in remote, Github repository, make sure you are not sending over any sensitive information.

# 5. My enviroment

Below you can find information about versions of R and specific packages used to create this project. 

```{r envir}
sessionInfo()
```

