---
title: "SMI205 Replication Project (2023)"
author: "Your Student ID/number"
date: "22/05/2023"
output: 
  html_document: 
    code_download: true
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
      smooth_scroll: true
---

```{r start, include=FALSE}
# Opening key libraries first
library(rmarkdown)
library(knitr)
```

# [Project title here]

### Rpubs link: [copy Rpubs url address here]
### GitHub Repository: [add url here if you have created a data or code repository, if not delete this line]
### Study Preregistration form: [copy Rpubs url address here or delete]

## Information about this replication project
* Replication project based on paper [add full citation here and link to its published online version]
* Replication method (select one from below):
  + Used replication package available at [add citation + repository link here]
  + Used materials obtained from authors
  + Own replication following methods section of the paper
  + Other - explain

## Workspace setup {.tabset .tabset-pills}

### YAML settings

 output: </br>
  &nbsp; html_document: </br>
    &nbsp;&nbsp; code_download: true </br>
    &nbsp;&nbsp;&nbsp; toc: true </br>
    &nbsp;&nbsp;&nbsp; toc_depth: 2 </br>
    &nbsp;&nbsp;&nbsp; toc_float: </br>
      &nbsp;&nbsp;&nbsp;&nbsp; collapsed: false </br>
      &nbsp;&nbsp;&nbsp;&nbsp; smooth_scroll: true </br>

### Global settings of R chunks

```{r setup, include=TRUE}
# Global options
opts_chunk$set(echo=TRUE,
	             cache=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
```

### Libraries

```{r libraries, include=TRUE}
# All used libraries
library("rmarkdown")
library("knitr")
```

### Versions of used packages

```{r versions, echo=FALSE}
# Versions of used packages
packages <- c("rmarkdown", "knitr")
names(packages) <- packages
lapply(packages, packageVersion)
```

### My enviroment

```{r myR, echo=FALSE}
# What is my R version?
version[['version.string']]
```

## 1. Introduction

*Code and outputs are not included in the wordcount*

**500 words**

Critical and evidence-based reflections on the paper and your new research question(s). 

* Clearly state which claim (finding/argument) from the replicated paper you discuss or test robustness of any methodological assumptions. 
* What the authors argued, and what could be counter-argued, and why.
* Use at least 5 scientific references to support your critique and your idea for research extension. 

Refer to the four types of replications as discussed in Freese and Peterson (2017) and explain what aspects of the original research your replication tests.

Briefly summarise, what results you expected to find and preregistered.


## 2. Data and methods

### 2.1. Data

**250 words**

Transparently __describe data__ used in the original paper and in your replication project: full dataset names, years of data collection, sources (who created data), sample sizes, variables used in the model you replicate.

Embed R code to upload your data (recommendation - show code only using `results='hide'` in the chunk options). 

Remember to add all datasets with their doi number to the list of references. See examples in the conditions of use for the ESS data [here](https://www.europeansocialsurvey.org/data/conditions_of_use.html).

Report all steps you have undertaken in __data transformation__:

* Subsetting data by selecting a lower number of variables or excluding any cases.
* Merging data files.
* Steps in recoding and renaming all variables. 
* Embed R code below to present the steps in data manipulation. If this would be very long chunk of R code (over 1 page), show just some examples and hide the rest of the code in text (`include=FALSE` option). The entire code will be still displayed in Appendix 2. 

You __have to__ display some summary statistics of your key variables of interest. This could be done as a table/s or a graph/s presenting distribution of your dependent variable/s for the entire sample or by a group of interest, boxplots, correlation plots or graphs with means values.


### 2.2. Methods

**250 words**

Describe what methods were used in the original paper and what methods you used and why. 

Support any changes you made in the analytical strategy with literature and/or displaying any relevant data diagnostics. 

If suitable, embed statistical tests comparing model fit of both methods.


## 3. Results

**500 words**

Display and describe your research results.

Show R code and professionally looking outputs, e.g. tables prepared in `tab_model` or `stargazer` functions, or graphs as `coefplots` or predicted values.

Provide in-depth discussion and interpretation of your results.


## 4. Conclusions

**250 words**

Discuss you findings in the light of literature you introduced in the introduction.

Reflect why your results are similar/different from the original study. 


## References

**min. 5 scientific references, excluding the replicated paper**

Freese, J., & Peterson, D. (2017). Replication in social science. *Annual Review of Sociology*, 43, 147-165, [doi: 10.1146](https://www.annualreviews.org/doi/abs/10.1146/annurev-soc-060116-053450).

## Appendix

### Appendix 1. My enviroment (full information) 

```{r session}
# Detailed information about my environment
sessionInfo()
```

### Appendix 2. Entire R code used in the project

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
